### 2020-01-13 README.Rmd
start a vignette

---
output: github_document
bibliography: inst/references.bib
nocite: | 
  @brenning2012, @valavi2018
---

@@

| Literature             | Package                                                   | Reference     | Class Name           | mlr3 sugar            |
| ---------------        | ---------                                                 | ---------     | -------------------- | --------------------- |
| Spatial Buffering      | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVBuffer` | `rsmp("spcv-buffer")` |
| Spatial Blocking       | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVBlock`  | `rsmp("spcv-block")`  |
| Spatial CV             | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResampleSpCVCoords` | `rsmp("spcv-coords")` |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVEnv`    | `rsmp("spcv-env")`    |

>>>>

---
output: github_document
bibliography: inst/references.bib
nocite: | 
  @brenning2012, @valavi2018, @schratz2019
---

@@

| Literature             | Package                                                   | Reference     | Class Name                      | mlr3 Sugar                     |
| ---------------        | ---------                                                 | ---------     | --------------------            | ---------------------          |
| Spatial Buffering      | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBuffer`          | `rsmp("spcv-buffer")`          |
| Spatial Blocking       | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBlock`           | `rsmp("spcv-block")`           |
| Spatial CV             | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResamplingSpCVCoords`          | `rsmp("spcv-coords")`          |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVEnv`             | `rsmp("spcv-env")`             |
| ---                    | ---                                                       | ---           | ---                             | ---                            |
| Repeated Spatial CV    | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `RepeatedRResamplingSpCVCoords` | `rsmp("repeated-spcv-coords")` |
